### 2020-01-30 wuhan.tex
stuff

>>>>

More broadly, disease modelers should always consider uncertainties in the data generating processes.
Process vs obs noise.

Our results indicate that the uncertainty in the estimates of the exponential growth rate $r$ matters the most.
However, as the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will eventually decrease, 
and the effect of uncertainty in the mean generation time will become more important.
